Evolutionary rescue and reintroduction of resistant frogs allows recovery in the presence of a lethal fungal disease

### 2023-05-20 doc/manuscript/translocation_bioarxiv.tex
Recompile PNAS version with new changes

To determine whether MYL frog populations show an evolutionary response
to Bd, we compared frog genomes between populations with contrasting
histories of Bd exposure. Specifically, we compared frog genomes sampled
in four populations that have not yet experienced a Bd-caused epizootic
(``naive'') \citep{zhou2015} versus in five populations that experienced
a Bd epizootic during the past several decades and have since recovered
to varying degrees (``recovering''; Figure~\ref{fig-allelefrequencies})
\citep{knapp2016, vredenburg2010}. These recovering populations exist in
an enzootic state \citep{briggs2010}, characterized by high Bd
prevalence and, in adults, moderate Bd infection intensity (``load'')
that is typically well below the level expected to cause mortality
\citep{vredenburg2010}. (See SI Appendix for additional details
regarding the study design.)

@@

Estimates of frog survival during the 1-year period following
translocation indicate that survival was highly variable between
recipient sites, but relatively constant within recipient sites (for the
subset of sites that received multiple translocations;
Figure~\ref{fig-translocation-survival}). As such, the average survival
of frogs in the first translocation to a site was an important predictor
of survival of frogs in subsequent translocations to that site
(Figure S4). This suggests an important
effect of site characteristics and/or (site * frog) interactions on frog
survival. In addition, 1-year survival was higher for frogs translocated
later in the study period than earlier
(Table S1), which we suggest resulted
primarily from our improved ability to choose recipient sites with
higher habitat quality for \emph{R. sierrae}. Finally, Bd loads were
fairly consistent before versus after translocation and loads were
nearly always well below the level indicative of severe chytridiomycosis
and associated frog mortality (Figure S5)
\citep{joseph2018, vredenburg2010}. Additional details on methods used
to estimate Bd loads are provided in the SI Appendix.

>>>>

To determine whether MYL frog populations show an evolutionary response
to Bd, we compared frog genomes between populations with contrasting
histories of Bd exposure. Specifically, we compared frog genomes sampled
in 4 populations that have not yet experienced a Bd-caused epizootic
(``naive'') \citep{zhou2015} versus in 5 populations that experienced a
Bd epizootic during the past several decades and have since recovered to
varying degrees (``recovering''; Figure~\ref{fig-allelefrequencies})
\citep{knapp2016, vredenburg2010}. These recovering populations exist in
an enzootic state \citep{briggs2010}, characterized by high Bd
prevalence and, in adults, moderate Bd infection intensity (``load'')
that is typically well below the level expected to cause mortality
\citep{vredenburg2010}. (See SI Appendix for additional details
regarding the study design.)

@@

Estimates of frog survival during the 1-year period following
translocation indicate that survival was highly variable between
recipient sites, but relatively constant within recipient sites (for the
subset of sites that received multiple translocations;
Figure~\ref{fig-translocation-survival}). As such, the average survival
of frogs in the first translocation to a site was an important predictor
of survival of frogs in subsequent translocations to that site
(Figure S4). This suggests an important
effect of site characteristics and/or (site * frog) interactions on frog
survival. In addition, 1-year survival was higher for frogs translocated
later in the study period than earlier
(Table S1), which we suggest resulted
primarily from our improved ability to choose recipient sites with
higher habitat quality for \emph{R. sierrae}. Finally, Bd loads were
fairly consistent before versus after translocation and loads were
nearly always well below the level indicative of severe chytridiomycosis
and associated frog mortality (Figure S5)
\citep{joseph2018, vredenburg2010}.
